---
title: "Hossain Interview 2"
author: "Hossain Morshed"
date: "1/16/2022"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## we have two data table. Go
```{r}
rm(list=ls(all=TRUE))
```


```{r}
if(!require("tidyverse")){
  install.packages("tidyverse")
}

library(tidyverse)
library(ggplot2)
```

## we have two data table
- First data table, which is 'Sagsbehandlingsdata'

```{r}
library(readxl)
case_table<-read_excel('Sagsbehandlingsdata.xlsx')
head(case_table)

```

- Second data table 'Tidsregistreringsdata'
```{r}
time_table<-read_excel('Tidsregistreringsdata.xlsx')
head(time_table)
```

```{r}
glimpse(case_table)
```

## Summary of the dataset
- Summary of 'Sagsbehandlingsdata'
```{r}
summary(case_table)
```
- Summary of 'Tidsregistreringsdata'
```{r}
summary(time_table)
```

```{r}
colSums(is.na(case_table))
```

```{r}
colSums(case_table=="")
```

## Total number of control is 10000
Total number of control which is completed 4452\
Total number of control which is not completed 5548
```{r}
case_table %>% count(`Afsluttet med træf`)%>%rename(Total=n)
```
- 0 = Complete
- 1 = Not Complete

## Total number of each control 
- we have 10 different type of control
- k04 type of control repeted most which is 4025
- k02 type of control repeted less which is only 5 times
- below chart show total number of control and how many of them are done
```{r}
a<-case_table %>% count(Kontroltype)%>% rename(total_number = n )
a
a%>%summarise(max=max(total_number),min=min(total_number))

```


```{r}
b<-case_table %>% filter(`Afsluttet med træf`==1)%>%count(Kontroltype)%>% rename(total_control_done = n )
```


```{r}
merge(a,b)
```


```{r}
df_control<-merge(a,b)
```


```{r}
df_control <- gather(df_control, event, total, total_number:total_control_done)
#df_control
```

## Graph show total number of control and control which is completed
```{r}
ggplot(df_control, aes(Kontroltype, total, fill=event)) + geom_bar(stat = "identity", position = 'dodge')  + ggtitle("Comparision between total control and total_control_done")+ geom_text(aes(label=total), vjust=-0.3, size=3.5,check_overlap = TRUE,angle = 0, position = position_dodge(.9))+theme_minimal()

```

## Total Revenue

-Total money need to collect is 173741135\
-Total money need to refund is 7697249\
-Total Revenue is 166043886

```{r}
case_table%>%summarise(total_money_collect=sum(`Provenu af kontrol`[which(case_table$`Provenu af kontrol`>0)]),total_money_refund=sum(`Provenu af kontrol`[which(case_table$`Provenu af kontrol`<0)]),total_revenue=sum(`Provenu af kontrol`))
#sum(case_table$`Provenu af kontrol`[which(case_table$`Provenu af kontrol`>0)])
#sum(case_table$`Provenu af kontrol`[which(case_table$`Provenu af kontrol`<0)])
#sum(case_table$`Provenu af kontrol`)
#case_table %>% colSums (case_table$`Provenu af kontrol`)
```


```{r}
s_t_money<-case_table %>% filter(`Afsluttet med træf`==1)%>% arrange((Sagsbehandler)) %>%group_by(Sagsbehandler)%>%summarise(total_amount_collect = sum(`Provenu af kontrol`[which(`Provenu af kontrol`>0)]))
```


```{r}
s_t_refund<-case_table %>% filter(`Afsluttet med træf`==1)%>% arrange((Sagsbehandler)) %>%group_by(Sagsbehandler)%>%summarise(Total_amount_refund = sum(`Provenu af kontrol`[which(`Provenu af kontrol`<0)]))
```

```{r}
merge(s_t_money,s_t_refund)
merge_collect_refund<-merge(s_t_money,s_t_refund)
```

```{r}
total_revenue<-case_table %>% filter(`Afsluttet med træf`==1)%>% arrange((Sagsbehandler)) %>%group_by(Sagsbehandler)%>%summarise(Total_revenue = sum(`Provenu af kontrol`))
```

## Each case office and total amount of money to collect
Total amount of money each case officer has to collect, refund and finally total revenue
```{r}
merge(merge_collect_refund,total_revenue)
collect_refund_revenue<-merge(merge_collect_refund,total_revenue)
```

```{r}
#collect_refund_revenue%>%summarise(avg = mean(total_amount_collect))
summary(collect_refund_revenue)
```

## Employee who has to collect most of the money
- we catagorise top case worker based on mean and median value\
top case worker who falls above mean value. we can see that total 6 case worker fall above the mean line. and they have to collect total 145713469 out of 173741135 which is 83.86815 %\
we can see that total 10 case worker fall above the median line. and they have to collect total 167262849 out of 173741135 which is 96.2713 %\

```{r}

collect_refund_revenue%>%arrange(desc(total_amount_collect))%>% filter(total_amount_collect>mean(total_amount_collect))
top_6_sag<-collect_refund_revenue%>%arrange(desc(total_amount_collect))%>% filter(total_amount_collect>mean(total_amount_collect))
collect_refund_revenue%>%arrange(desc(total_amount_collect))%>% filter(total_amount_collect>mean(total_amount_collect))%>%summarise(sum_of_total_amount_collect = sum(total_amount_collect))
print(" ")

collect_refund_revenue%>%arrange(desc(total_amount_collect))%>% filter(total_amount_collect>median(total_amount_collect))
collect_refund_revenue%>%arrange(desc(total_amount_collect))%>% filter(total_amount_collect>median(total_amount_collect))%>%summarise(sum_of_total_total_amount = sum(total_amount_collect))
#collect_refund_revenue%>%arrange(desc(total_amount_collect))%>%top_n(5,total_amount_collect)
#collect_refund_revenue%>%arrange(desc(total_amount_collect))
```



```{r}
(145713469/173741135)*100
(167262849/173741135)*100
```


```{r}
# spread employee time table
spread(time_table,Aktivitet,Timer)
time_table_spread1<-spread(time_table,Aktivitet,Timer)
```

# pairs.panels() - lists correlations, histograms and scatter plots on the same matrix
```{r}
psych::pairs.panels(time_table_spread1)

```
we can see that actual work time has a negative corelation with course and meetings which is -.29 and -.64
ferie and course has negative correlation which is -.61 which means if one oncrease othe decrease.
seek and meating has negative correlation which is -.35


```{r}
# seperate top 6 employee time table
time_table_spread<-time_table_spread1%>%rename(Sagsbehandler=Medarbejdernummer)
top_6_sag_time<-merge(top_6_sag,time_table_spread,all.x = TRUE)
top_6_sag_time%>%arrange(desc(total_amount_collect))%>%select(-total_amount_collect,-Total_amount_refund,-Total_revenue)
```
psych::pairs.panels(time_table_spread1)




```{r}
case_table %>% filter(`Afsluttet med træf`==1)%>% arrange((Sagsbehandler)) %>%group_by(Sagsbehandler,Kontroltype)%>%summarise(`Provenu af kontrol` = sum(`Provenu af kontrol`[which(`Provenu af kontrol`>0)]))
```

## Each control type and total amount of money 
- below table show each control type and total amount of money need to collect.


```{r}
case_table %>% filter(`Afsluttet med træf`==1)%>% arrange((Sagsbehandler)) %>%group_by(Kontroltype)%>%summarise(total_amount = sum(`Provenu af kontrol`[which(`Provenu af kontrol`>0)]))
c_money<-case_table %>% filter(`Afsluttet med træf`==1)%>% arrange((Sagsbehandler)) %>%group_by(Kontroltype)%>%summarise(total_amount = sum(`Provenu af kontrol`[which(`Provenu af kontrol`>0)]))
```

## comparision total amount and each type of control
- we can see that most amount of money we need to collect is k04 type of control.
```{r}
ggplot(c_money, aes(Kontroltype, total_amount)) + geom_bar(stat = "identity",fill="steelblue") + geom_text(aes(label=total_amount), vjust=-0.3, size=3.5)+theme_minimal() + ggtitle("Comparision between Kontrol type and total amount")
```

```{r}
case_table %>% filter(`Afsluttet med træf`==1 & Kontroltype=='K04' & (`Provenu af kontrol`>0))%>%group_by(Sagsbehandler)%>%summarise(k04_Total_amount = sum(`Provenu af kontrol`[which(`Provenu af kontrol`>0)]))%>%arrange(desc(k04_Total_amount))

k04_type_top_employee<-case_table %>% filter(`Afsluttet med træf`==1 & Kontroltype=='K04' & (`Provenu af kontrol`>0))%>%group_by(Sagsbehandler)%>%summarise(k04_Total_amount = sum(`Provenu af kontrol`[which(`Provenu af kontrol`>0)]))%>%arrange(desc(k04_Total_amount))
```


## Top 6 employee who has to collect k04 type control
```{r}
k04_type_top_employee%>%filter(k04_Total_amount>mean( k04_Total_amount))
k04_type_top6<-k04_type_top_employee%>%filter(k04_Total_amount>mean( k04_Total_amount))
```


```{r}
top_6_employee_totalamount_k4<-full_join(top_6_sag, k04_type_top6, by = "Sagsbehandler")
full_join(top_6_sag, k04_type_top6, by = "Sagsbehandler")
```

- who are also the same top 6 employee who have to collect total amount  
```{r}
top_6_employee_totalamount_k4%>%mutate(percentage=(k04_Total_amount/total_amount_collect)*100)%>%select(-Total_amount_refund,-Total_revenue)
```

## which kind of control mostly done

```{r}
case_table %>% filter(`Afsluttet med træf`==0) %>%group_by(Kontroltype)%>%count(Kontroltype)%>%rename(total_number = n)
most_done_kontrol<-case_table %>% filter(`Afsluttet med træf`==0) %>%group_by(Kontroltype)%>%count(Kontroltype)%>%rename(total_number = n)

```

- Bar chart of completed control
```{r}
ggplot(most_done_kontrol, aes(Kontroltype,total_number,fill=Kontroltype)) + geom_bar(stat="identity", width=1,color="white") + geom_text(aes(label=total_number), vjust=-0.3, size=3.5)
```
## Total time spend by employee in different activities

```{r}
time_table %>%group_by(Aktivitet)%>% summarise(total_time=sum(Timer))
```

- Actual work time spend by different employee
```{r}
ggplot(time_table_spread, aes(Sagsbehandler, `Sagsbehandling med kontrol`, fill = Sagsbehandler)) + 
  geom_point()+geom_bar(stat="identity", width=1)
```

```{r}
time_table_spread%>%summarise(Avg_Ferie=mean(Ferie),Avg_Kontormøder=mean(Kontormøder),Avg_Kursusdeltagelse=mean(Kursusdeltagelse),Avg_work_time=mean(`Sagsbehandling med kontrol`),Avg_Sygdom=mean(Sygdom))

```


```{r}
top_6_sag_time%>%arrange(desc(total_amount_collect))%>%select(-total_amount_collect,-Total_amount_refund,-Total_revenue)
```


```{r}
top_6_sag_timetable<-top_6_sag_time%>%arrange(desc(total_amount_collect))%>%select(-total_amount_collect,-Total_amount_refund,-Total_revenue)
```

  
  
```{r}
#time_table
mean_df_timetable<-time_table %>% group_by(Aktivitet)%>%summarise(mean_val=mean(Timer))
time_table %>% group_by(Aktivitet)%>%summarise(mean_val=mean(Timer))
```
  
```{r}
top_6_sag_timetable%>%gather("Aktivitet","time",2:6)%>%ggplot(., aes(Sagsbehandler, time,col=Aktivitet,group = 1))+geom_point()+geom_line()+facet_wrap(~Aktivitet)+geom_hline(mean_df_timetable,mapping =aes(yintercept=mean_val,col=Aktivitet))

```



```{r}
psych::pairs.panels(top_6_sag_timetable)
```


## each employee overview of control
```{r}
#case_table %>% arrange((Sagsbehandler))%>%group_by(Sagsbehandler)

s1<-case_table %>% arrange((Sagsbehandler))%>%group_by(Sagsbehandler)%>% distinct(Kontroltype)%>%count(Sagsbehandler)%>%rename(assigned_control=n)# need this one

s2<-case_table %>% arrange((Sagsbehandler))%>%group_by(Sagsbehandler)%>%count(Sagsbehandler)%>%rename(assigned_work=n)
s3<-case_table %>% arrange((Sagsbehandler))%>%filter(`Afsluttet med træf`== 0)%>%count(Sagsbehandler)%>%rename(completed_work=n)

s4<-case_table %>% arrange((Sagsbehandler))%>%filter(`Afsluttet med træf`== 1)%>%count(Sagsbehandler)%>%rename(incomplete_work=n)
s5<-merge(s1,s2)
#merge(s5,s3,all.x = TRUE)
s6<-merge(s5,s3,all.x = TRUE)
case_officer_table1<-merge(s6,s4,all.x = TRUE)

case_officer_table1[is.na(case_officer_table1)] <- 0
case_officer_table1
#zz[is.na(zz)] <- 0

#merge(x = df1, y = df2, by = "CustomerId", all.x = TRUE)
```



```{r}
#top_6_sag_time
target <- c("W05", "W07","W08","W15","W17","W19")
case_officer_table1%>%filter(Sagsbehandler %in% target)
```
We can see that top 6 case worker who are responsible to collect 84% of total revenue
are able to work almost 10 type of control out of 10 control.



We can see from our small analysis that these 6 employees are the most skilled employees, 
can work All types of control, that’s why they are responsible to collect most of the revenue.
Through proper training and course work, we can increase the rest of the employee's skills 
so the task can be distributed to the rest of the employees as well.

To find more insight from the dataset we need to do more analysis.

```{r}

```


```{r}

```



```{r}

```


```{r}

```



```{r}

```


```{r}

```











